Tasks:
Quantitative Analysis - Backtesting Investment Portfolios:
* Use reproductive code based on selection criteria to realize quarterly investments.
* Use Quantmod package to extract and calculate ratios from three financial statements.
* Select top 10 performance stocks of each industry quarterly from 1980 to 2017.
* Design portfolios according to ratios of different investment perspective.
* Improve portfolio annual returns by 3.1 percent compare to benchmark of S&P 500.

Skills：
  Basic:
    * data manipulation
    * vectorize calculation
    * Apply methods
    * 
  Advanced:
    * 
  

STEP 0: set up target data
Get Online datasets
```{r}
library(quantmod)
library(tictoc)
local=getwd()
setwd(local)
start=Sys.time()
dat= readRDS('datasets.RDS')
dat_temp= dat

new_dates= c("1988-03")
years=c(1988:2017)

month=c("03","06","09","12")
for(i in years){
  for(j in month){
    new_dates=c(new_dates,paste(i,j,sep="-"))
  }
}
new_dates=as.character(new_dates)[2:length(new_dates)]

new_date= c(198803)
years=c(1988:2017)
month=c("03","06","09","12")
for(i in years){
  for(j in month){
    new_date=c(new_date,paste(i,j,sep=""))
  }
}
new_date=as.integer(new_date)[2:length(new_date)]

```



Methods for Ratio groups in 8 consecutive terms
```{r}
### Break line After get a table with stocks as rows, period as columns
clean_up=function(dat){
  dat[is.na(dat) |is.infinite(dat)]=0
  return(dat)
}
getROC <- Vectorize(function(x){
  ROC_temp      <-dat[dat$PRIME==x,]$ROC
  if (length(ROC_temp)<8){
    return(0)
  }
  inside<- ROC_temp + 1
  ROC8<- prod(inside)^(1/8)-1
  ROC8[is.na(ROC8) | is.infinite(ROC8)] = 0 
  return(ROC8)
})
getROA <- Vectorize(function(x){
  ROA_temp      <-dat[dat$PRIME==x,]$ROA
  if (length(ROA_temp)<8){
    return(0)
  }
  value<- ROA_temp + 1
  ROA8<- prod(value)^(1/8)-1
  ROA8=clean_up(ROA8)
  return(ROA8)
})

filter_portfolio=function(ratio,tick){
  df_=data.frame(ratio,tick)
  df_=df_[order(df_$ratio,decreasing = TRUE),]
  result=rbind(head(df_,10),tail(df_,10))
  return(result)
}

getCFOA <- Vectorize(function(x){
  CFOA_temp      <-dat[dat$PRIME==x,]$`Free Cash Flow`
  if (length(CFOA_temp)<8){
    return(0)
  }
  value=sum(CFOA_temp)/dat[dat$PRIME==x,]$`Total Assets`[1]
  value=clean_up(value)
  return(value)
})

getMS <- Vectorize(function(x){
  MS_temp     <-dat[dat$PRIME==x,]$GM
  if (length(MS_temp)<8){
    return(0)
  }
  value=mean(MS_temp)/sd(MS_temp)
  value=clean_up(value)
  return(value)
})

getMG <- Vectorize(function(x){
  MG_temp      <-dat[dat$PRIME==x,]$GM
  if (length(MG_temp)<8){
    return(0)
  }
  value=(1+(MG_temp[2]/MG_temp[1]))*(1+(MG_temp[3]/MG_temp[2]))*(1+(MG_temp[4]/MG_temp[3]))*
    (1+(MG_temp[5]/MG_temp[4]))*(1+(MG_temp[6]/MG_temp[5]))*(1+(MG_temp[7]/MG_temp[6]))*(1+(MG_temp[8]/MG_temp[7]))
  value=value^(1/7)-1
  value=clean_up(value)
  return(value)
})
```


STEP 1
Period
```{r}
time=new_date[1:8]
STEP1=function(time){
  df=subset(dat_temp, dat_temp$Date>=time[1] & dat_temp$Date<=time[8])
  filter=aggregate(Date~PRIME,df,NROW)
  tick=filter[filter$Date ==8,]$PRIME
  #STEP 1 getPROBM within loop
  # PROBM :  GPMI, AQI, LVGI, TATA, 
  dat=subset(df,df$PRIME %in% tick &df$Date %in% c(time[7],time[8]))
  dat$GPMI_ = (dat$`Gross Profit`/dat$Revenue)
  dat$AQI_ = (dat$`Total Assets` - dat$`Total Current Assets` - (dat$`Gross Property, Plant And Equipment` + dat$`Accumulated Depreciation`))/dat$`Total Assets`
  dat$LVGI_ = (dat$`Shares Outstanding (Eop)` * dat$`Total Debt Per Share`)/dat$`Total Assets`
  dat$TATA_ = (dat$`Operating Income` - dat$`Cash Flow From Operations`)/dat$`Total Assets`
  a = subset(dat,Date == time[7])
  b = subset(dat,Date == time[8])
  c = merge(a,b,by='PRIME')
  c$gpmi = c$GPMI_.x/c$GPMI_.y
  c$aqi = c$AQI_.x/c$AQI_.y
  c$sgi = c$Revenue.x/c$Revenue.y
  c$depi = c$`Depreciation, Depletion And Amortization.x`/c$`Depreciation, Depletion And Amortization.y`
  c$sgai = c$`Selling, General, & Admin. Expense.y`/c$`Selling, General, & Admin. Expense.x`
  c$lvgi = c$LVGI_.y/c$LVGI_.x
  c$tata = c$TATA_.y/c$TATA_.x
  for(i in 58:64){
    c[,i]=clean_up(c[,i])
  }
  c$total = c$gpmi+c$aqi+c$sgi+c$depi+c$sgai+c$lvgi+c$tata
  df3= subset(c,total <= 7 & total >= 0, c('PRIME','total'))
  tick = df3$PRIME
  return(tick)
}

```

STEP 2
```{r}

STEP2=function(tick,time){
  df=dat_temp[dat_temp$Date>=time[1] & dat_temp$Date<=time[8],]
  df2=subset(df, df$PRIME %in% tick)
  dat=df2
  ROC         <- dat$`Operating Income`/(dat$`Gross Property, Plant And Equipment` +
                                           dat$`Accumulated Depreciation` +
                                           dat$`Total Current Assets` -
                                           dat$`Total Current Liabilities`)
  ROC[is.na(ROC) | is.infinite(ROC)] <- 0
  dat$ROC=ROC
  ROC<-getROC(tick)
  o1=filter_portfolio(ROC,tick)
  ROA=dat$`Net Income`/dat$`Total Assets`
  ROA=clean_up(ROA)
  dat$ROA=ROA
  ROA=getROA(tick)
  o2=filter_portfolio(ROA,tick)
  CFOA=getCFOA(tick)
  o3=filter_portfolio(CFOA,tick)
  GM=dat$`Gross Profit`/dat$Revenue
  dat$GM=GM
  
  MG=getMG(tick)
  MS=getMS(tick)
  o4=filter_portfolio(MG,tick)
  o5=filter_portfolio(MS,tick)
  table=rbind(o1,o2,o3,o4,o5)
  tickers=as.character(table$tick)
  return(tickers)
}
```


```{r}
df4=matrix(nrow=100,ncol=113)
for(j in 8:length(new_date)){
  time=new_date[(j-7):(j+1)]
  # df used for ratios calculation
  ticker=STEP1(time)
  tickers=STEP2(ticker,time)
  returns=c()
  for(i in 1:100){
    tryCatch({
      
      price=getSymbols(tickers[i],auto.assign = FALSE,from='1988-03-01',to='2017-12-29')[,6]
      return(price)
    },error=function(e){
      return(NA)
    })
    tryCatch({
      v=as.vector(last(price[new_dates[j]]))
    },error=function(e){
      return(NA)
    })
    tryCatch({
      v2=as.vector(last(price[new_dates[j+1]]))
      ratio=(v2-v)/v
      return(ratio)
    },error=function(e){
      return(NA)
    })
    returns=c(returns,ratio)
  }
  returns[is.na(returns)]=0
  port_return=c()
  port_return[1]=mean(returns[1:10])
  port_return[2]=mean(returns[11:20])
  port_return[3]=mean(returns[21:30])
  port_return[4]=mean(returns[31:40])
  port_return[5]=mean(returns[41:50])
  port_return[6]=mean(returns[51:60])
  port_return[7]=mean(returns[61:70])
  port_return[8]=mean(returns[71:80])
  port_return[9]=mean(returns[81:90])
  port_return[10]=mean(returns[91:100])
  df4[,j-7]=port_return
}
df4=clean_up(df4)
df5=sapply(1:112,function(x){return(rank(df4[,x]))})

count=function(df,num){
  count_list=c()
  for(i in 1:nrow(df)){
    count=0
    for(j in 1:ncol(df)){
      if(df[i,j]==num){
        count=count+1
      }
    }
    count_list=c(count_list,count)
  }
  return(count_list)
}
```




```{r}
### After get a table with stocks as rows, period as columns
Portfolio=c("roc1","roc2","roa1","roa2","cfoa1","cfoa2","mg1","mg2","ms1","ms2")
Pos=sapply(1:10,function(x){return(length(which(df4[x,]>0)))})
Neg=sapply(1:10,function(x){return(length(which(df4[x,]<0)))})
Wins=c(count(df5,1))
Lost=c(count(df5,10))

Rank=sapply(1:10,function(x){return(mean(df5[x,]))})

Gmean=sapply(1:10,function(x){
  v=df4[x,]
  v=v+1
  return(prod(v)^(1/112)-1)
})
Amean=sapply(1:10,function(x){v=df4[x,]
return(mean(v))})

final_df=data.frame(Portfolio,Pos,Neg,Rank,Wins,Lost,Gmean,Amean)
final_df

```

